---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# YarraWaterAnalysis


<!-- badges: start -->

<!-- badges: end -->

The `YarraWaterAnalysis` package provides tools for analyzing and visualizing streamflow data from the Yarra River at McMahons monitoring site.

## Installation
You can install the development version of YarraWaterAnalysis from [GitHub](https://etc5523-2025.github.io/assignment-4-packages-and-shiny-apps-ChenLiu0123/) with:

```{r  }
# install.packages("devtools")
# devtools::install_github("ETC5523-2025/assignment-4-packages-and-shiny-apps-ChenLiu0123")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r  }
library(YarraWaterAnalysis)
## basic example code
```
 
## Calculate Flow Statistics

```{r}
calculate_flow_stats(yarra_water_data)
```

You can use this function to calculate basic statistics for Yarra River streamflow data

## analyze_seasonal_patterns

```{r}
# Analyze seasonal patterns
seasonal_stats <- analyze_seasonal_patterns(yarra_water_data)
print(seasonal_stats)

```

You can use this function to analyze seasonal patterns


## detect_high_flow_events


```{r, echo=FALSE}
# Detect high flow events
high_flows <- detect_high_flow_events(yarra_water_data, threshold = 200)
head(high_flows)
```

You can use this function to detect high flow event



## Interactive Exploration

Launch the Shiny application for interactive data exploration:

```{r}
# Launch the interactive app
# launch_app()
```


The Shiny app provides:

- Interactive time series visualization
- Seasonal pattern analysis
- Flow duration curves
- Statistical summaries
- Data filtering capabilities 
